The Driving Forces of API Evolution

### 2015-06-02 thesis/paper.tex
Changes to layout and inclusions to bib

\subsubsection{APIs as Systems}
Motivate why APIs are systems

@@

\subsubsection{Types of Software Evolution}
A set of four categories describing different kinds of software maintenance \cite{lientz1980software} became the basis upon which twelve new types were developed \cite{chapin2001types}. The twelve types of software evolution and software maintenance, as seen in Table \ref{table:expl_types}, describe a software evolution activity that relates to one of three particular areas; the code, the software and the customer-experienced functionality.

@@

\subsubsection{Lehman’s Laws}
Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws. The laws are presented in Table \ref{table:expl_laws}. The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world. Two other types of systems are also identified; S-type systems and P-type systems. S-type systems are programs which are exactly derivable from a specification. An example of such a program is one which finds the lowest common denominator for two integers. An example of a P-type system is a chess program. These types of programs can be derived from a specification, but the rules of the program have to be abstracted. In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible. Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes. It is therefore not possible to create an exact specification of any non-trivial API.

\subsection{API Evolution} \label{related_work}
The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring, shi2011empirical} and Smalltalk \cite{robbes2012developers}. Attempts to uncover the intents of the changes made in the Java libraries, AWT and Swing, have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.

Investigations of three frameworks and one library indicated that 80\% of refactoring changes to APIs negatively affected existing applications \cite{dig2005role}. The changes, sometimes referred to as ripple effects \cite{robbes2012developers} indicate that negative effects of changes can propagate throughout a software ecosystem. It was found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.

>>>>

\subsubsection{APIs as Systems}
Motivate why APIs are systems
\cite{761853,5733835}

@@

A set of four categories describing different kinds of software maintenance \cite{lientz1980software} became the basis upon which twelve new types were developed \cite{chapin2001types}. The twelve types of software evolution and software maintenance, as seen in Table \ref{table:expl_types}, describe a software evolution activity that relates to one of three particular areas; the code, the software and the customer-experienced functionality.

@@

Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws. The laws are presented in Table \ref{table:expl_laws}. The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world. Two other types of systems are also identified; S-type systems and P-type systems. S-type systems are programs which are exactly derivable from a specification. An example of such a program is one which finds the lowest common denominator for two integers. An example of a P-type system is a chess program. These types of programs can be derived from a specification, but the rules of the program have to be abstracted. In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible.

\subsection{API Evolution} \label{related_work}
The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring, shi2011empirical} and Smalltalk \cite{robbes2012developers}. Attempts to uncover the intents of the changes made in the Java libraries, AWT and Swing, have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}. Investigations of three frameworks and one library indicated that 80\% of refactoring changes to APIs negatively affected existing applications \cite{dig2005role}. The changes, sometimes referred to as ripple effects \cite{robbes2012developers} indicate that negative effects of changes can propagate throughout a software ecosystem. It was found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.

\subsubsection{APIs as E-Type Systems}
Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes. It is therefore not possible to create an exact specification of any non-trivial API.
